\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-29 grassposter/2015_EGU_G7_Python/main.tex
2015_EGU_G7_Python poster: minor cleanup; parser text addition
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64927 15284696-431f-4ddb-bdfa-cd5b030d7da7

% License: CC0
% The license is CC0 but you can acknowledge the authors if you want to. See their names bellow.

@@

\block{\blocktitlewrap{More information}}{
\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation
\end{minipage}
\\
% http://grass.osgeo.org/
\url{grass.osgeo.org}
&
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals/libpython}
\end{tabular}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Temporal framework}}{
\cite{Gebbert2014}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS Addons}}{
The GRASS GIS Addons ensures long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS itself.
}

The GRASS GIS library has a C API which is often used to create GRASS modules in C and C++.

GRASS GIS modules can be used in R using \pkg{rgrass7} package.
}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{osgeo}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
\end{minipage}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
\end{minipage}

@@

Luca Delucchi contributed significantly to development of Python interfaces for GRASS GIS
by extensive testing in early stages of development, documenting the APIs
and general contributions to the code itself.
}

@@

\bibitem{Neteler2012}
  Neteler, M., Bowman, M. H., Landa, M., Metz, M., 2012.
  \emph{GRASS GIS: A multi-purpose open source GIS.}
  Environmental Modelling \& Software, 31(0), 124-130.

\bibitem{Gebbert2014}
  Gebbert, S., Pebesma, E., 2014. A temporal GIS for field based environmental modeling. Environmental
  Modelling \& Software 53, 1-12.

@@

\bibitem{Zambelli2013}
  Zambelli, P., Gebbert, S., Ciolli, M., 2013. Pygrass: An Object Oriented Python Application Programming
  Interface (API) for Geographic Resources Analysis Support System (GRASS) Geographic Information System
  (GIS). ISPRS International Journal of Geo-Information 2, 201-219.

>>>>

% License: CC0
% The license is CC0 but you can acknowledge the authors if you want to. See their names below.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS Addons}}{
The GRASS GIS Addons ensure long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS core.
}

The GRASS GIS library povides a C API which is commonly used to create GRASS modules in C and C++.

GRASS GIS modules can be used within R using the \pkg{rgrass7} package.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{More information}}{
\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation
\end{minipage}
\\
% http://grass.osgeo.org/
\url{grass.osgeo.org}
&
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals/libpython}
\end{tabular}

@@

The g.parser module provides full parser support for GRASS GIS scripts.
It provides the creation of help page template, and command line option
checking. Each command and scripts which uses the GRASS GIS parser can
publish its parameter and flags description in XML. Through the included
XML parser this description can be turned into a graphical user interface with
standardized styling.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS 7 Temporal Framework}}{
The GRASS GIS Temporal Framework offers the temporal GIS functionality of GRASS GIS 
and provides a Python API to implement spatio-temporal processing modules. 
The framework introduces space-time datasets that represent time series of raster, 
3D raster or vector maps. Some API examples:
\includegraphics[width=1\linewidth, clip, trim=0 0 0 0]{tgrass_examples}
}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{osgeo}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
GRASS GIS is a OSGeo project. OSGeo provides infrastructure for project
Web sites, mailing lists and source code management.
\end{minipage}

@@

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code 2014.
\end{minipage}

@@

Luca Delucchi, Italy, contributed significantly to development of Python interfaces for GRASS GIS 7
through extensive testing in early stages of development, documenting the APIs
and general contributions to the code itself.
}

@@

\bibitem{Neteler2012}
  Neteler, M., Bowman, M. H., Landa, M., Metz, M., 2012.
  \emph{GRASS GIS: A multi-purpose open source GIS.}
  Environmental Modelling \& Software, 31, 124--130.

\bibitem{Gebbert2014}
  Gebbert, S., Pebesma, E., 2014. A temporal GIS for field based environmental modeling. Environmental
  Modelling \& Software 53, 1--12.

@@

\bibitem{Zambelli2013}
  Zambelli, P., Gebbert, S., Ciolli, M., 2013. Pygrass: An Object Oriented Python Application Programming
  Interface (API) for Geographic Resources Analysis Support System (GRASS) Geographic Information System
  (GIS). ISPRS International Journal of Geo-Information 2, 201--219.
